Randomized trace estimation for parameter-dependent matrices applied to spectral density approximation

### 2024-07-19 paper/re-pro-badge.tex
automatically reproduce paper

The code for our numerical experiments can be found on \url{https://github.com/FMatti/Rand-TRACE}. The figures and tables were generated from the commit \href{https://github.com/FMatti/Rand-TRACE/tree/bca2ff7}{bca2ff7} on 2024-07-18 at 14:29:53 UTC.

>>>>

The code for our numerical experiments can be found on \url{https://github.com/FMatti/Rand-TRACE}. The figures and tables were generated from the commit \href{https://github.com/FMatti/Rand-TRACE/tree/3aeb08c}{3aeb08c} on 2024-07-19 at 15:04:36 UTC.
